---
title: "R Notebook"
output: html_notebook
---

```{r}
syms<-c("000300.SH","000016.SH")

for(sy in syms){
  loadRData(sy)
}

alignSymbols(syms)





```

1. 指数不同点位下未来的收益
不同点位区间下，未来X天的收益，最大收益，最大亏损
最大收益和最大亏损计算有误，需调整
```{r}

source(file.path(substr(getwd(), 1, 22), "header.R"))

sym <- "000001.SH"
yieldDays <- 250


loadRData(sym)

applyInd(
  sym,
  fun.name = "Return.calculateX",
  arguments = list(x = get(sym), column = "close"),
  label = "dailyReturn"
)

applyInd(
  sym,
  fun.name = "rollapplyX",
  arguments = list(
    x = get(sym),
    column = "dailyReturn",
    width = yieldDays,
    FUN = "Return.cumulative"
  ),
  label = paste0("cumReturn", yieldDays, "D")
)

maxDrawdown.fromNow<-function(R,geometric=T){
  
  x = checkData(R)
    if (geometric) 
      Return.cumulative = cumprod(1 + x)
    else Return.cumulative = 1 + cumsum(x)
 min(0, min(Return.cumulative-1))
  
}

maxRunup.fromNow <- function(R,geometric=T){
  
  x = checkData(R)
    if (geometric) 
      Return.cumulative = cumprod(1 + x)
    else Return.cumulative = 1 + cumsum(x)
  max(Return.cumulative-1)
  
  
}



applyInd(
  sym = sym,
  fun.name = "rollapplyX",
  arguments = list(
    x = get(sym),
    column = "dailyReturn",
    width = yieldDays,
    FUN = "maxDrawdown.fromNow"
  ),
  label = paste0("maxDown", yieldDays)
)


applyInd(
  sym = sym,
  fun.name = "rollapplyX",
  arguments = list(
    x = get(sym),
    column = "dailyReturn",
    width = yieldDays,
    FUN = "maxRunup.fromNow"
  ),
  label = paste0("maxRunup", yieldDays)
)


applyInd(
  sym,
  fun.name = "leadX",
  arguments = list(
    x = get(sym),
    column = paste0("cumReturn", yieldDays, "D"),
    k = yieldDays
  ),
  label = paste0("leadR", yieldDays, "D")
)




applyInd(
  sym,
  fun.name = "leadX",
  arguments = list(
    x = get(sym),
    column = paste0("maxDown", yieldDays),
    k = yieldDays
  ),
  label = paste0("leadmaxD", yieldDays, "D")
)

applyInd(
  sym,
  fun.name = "leadX",
  arguments = list(
    x = get(sym),
    column = paste0("maxRunup", yieldDays),
    k = yieldDays
  ),
  label = paste0("leadmaxUp", yieldDays, "D")
) 

mydata<-as.data.frame(get(sym)[,c(4,5,8,13:15)])
names(mydata)<-c("close","pe","dividendyield","leadR","leadmaxD","leadmaxR")

mydata<-mydata%>%mutate(close.inter=cut(round(pe,0),15))%>%mutate(maxRD=leadmaxR/leadmaxD)

ydata<-mydata
rownames(ydata)<-index(get(sym))


ggplot(ydata,aes(x=close,y=leadR))+geom_point(shape=1,size=0.8)+
  geom_hline(aes(yintercept=0))+
  geom_vline(aes(xintercept=2900))+ggtitle("不同上证综指点位未来一年收益分布")
ggplot(ydata,aes(x=close,y=leadmaxR))+geom_point(shape=1,size=0.8)+
  geom_hline(aes(yintercept=0))+
  geom_vline(aes(xintercept=2900))+ggtitle("不同上证综指点位未来一年最大涨幅分布")
ggplot(ydata,aes(x=close,y=leadmaxD))+geom_point(shape=1,size=0.8)+
  geom_hline(aes(yintercept=0))+
  geom_vline(aes(xintercept=2900))+ggtitle("不同上证综指点位未来一年最大回撤分布")
ggplot(ydata[abs(ydata$maxRD)<5,],aes(x=close,y=maxRD))+geom_point(shape=1,size=0.8)+
  geom_hline(aes(yintercept=1))+
  geom_vline(aes(xintercept=2900))+ggtitle("不同上证综指点位未来一年最大涨幅比最大回撤分布")



ggplot(ydata,aes(x=pe,y=leadR))+geom_point(shape=1,size=0.8)+
  geom_hline(aes(yintercept=0))+
  geom_vline(aes(xintercept=13))+ggtitle("不同上证综指PE未来一年收益分布")
ggplot(ydata,aes(x=pe,y=leadmaxR))+geom_point(shape=1,size=0.8)+
  geom_hline(aes(yintercept=0))+
  geom_vline(aes(xintercept=13))+ggtitle("不同上证综指PE未来一年最大涨幅分布")
ggplot(ydata,aes(x=pe,y=leadmaxD))+geom_point(shape=1,size=0.8)+
  geom_hline(aes(yintercept=0))+
  geom_vline(aes(xintercept=13))+ggtitle("不同上证综指PE未来一年最大回撤分布")
ggplot(ydata[abs(ydata$maxRD)<10,],aes(x=pe,y=maxRD))+geom_point(shape=1,size=0.8)+
  geom_hline(aes(yintercept=1))+
  geom_vline(aes(xintercept=13))+ggtitle("不同上证综指点位未来一年最大涨幅比最大回撤分布")
  


```

1. 极端假设，没有择时择股能力，全凭运气
策略：买入一直持有至到期
```{r}


ggplot(ydata,aes(x=close,y=leadR))+geom_point(shape=1,size=0.8)+
  geom_hline(aes(yintercept=0))+
  geom_vline(aes(xintercept=2900))+ggtitle("不同上证综指点位未来一年收益分布")

groupdata.close<-ydata%>%mutate(close.cut=cut(close,seq(1000,6200,by = 200),dig.lab=0,labels=paste0(seq(1100,6200,by=200),"±100")))%>%group_by(close.cut)%>%
  summarise(mean.r=mean(leadR,na.rm=T),
            median.r=median(leadR,na.rm=T),
            sd.r=sd(leadR,na.rm=T),
            quantile10=quantile(leadR,0.1,na.rm=T),
            quantile90=quantile(leadR,0.9,na.rm=T),
            sharp.r=mean.r/sd.r)
groupdata.close
ggplot(groupdata.close,aes(x=close.cut,y=sharp.r))+geom_bar(stat="identity")+
  theme(axis.text.x=element_text(angle=90))+ggtitle("不同上证综指未来一年收益平均值分布")





ggplot(ydata,aes(x=pe,y=leadR))+geom_point(shape=1,size=0.8)+
  geom_hline(aes(yintercept=0))+
  geom_vline(aes(xintercept=13))+ggtitle("不同上证综指PE未来一年收益分布")

groupdata.pe<-ydata%>%mutate(pe.cut=cut(pe,seq(8,70,by = 2),dig.lab=0,labels=paste0(seq(9,69,by=2),"±1")))%>%group_by(pe.cut)%>%
  summarise(mean.r=mean(leadR,na.rm=T),
            median.r=median(leadR,na.rm=T),
            sd.r=sd(leadR,na.rm=T),
            quantile10=quantile(leadR,0.1,na.rm=T),
            quantile90=quantile(leadR,0.9,na.rm=T),
            sharp.r=mean.r/sd.r)

ggplot(groupdata.pe,aes(x=pe.cut,y=sharp.r))+geom_bar(stat="identity")+
  theme(axis.text.x=element_text(angle=90))+ggtitle("不同上证综指PE未来一年收益平均值分布")





ggplot(ydata,aes(x=dividendyield,y=leadR))+geom_point(shadividendyield=1,size=0.8)+
  geom_hline(aes(yintercept=0))+
  geom_vline(aes(xintercept=2.2))+ggtitle("不同上证综指dividendyield未来一年收益分布")

groupdata.dividendyield<-ydata%>%mutate(dividendyield.cut=cut(dividendyield,seq(8,70,by = 2),dig.lab=0,labels=paste0(seq(9,69,by=2),"±1")))%>%group_by(dividendyield.cut)%>%
  summarise(mean.r=mean(leadR,na.rm=T),
            median.r=median(leadR,na.rm=T),
            sd.r=sd(leadR,na.rm=T),
            quantile10=quantile(leadR,0.1,na.rm=T),
            quantile90=quantile(leadR,0.9,na.rm=T),
            sharp.r=mean.r/sd.r)

ggplot(groupdata.dividendyield,aes(x=dividendyield.cut,y=sharp.r))+geom_bar(stat="identity")+
  theme(axis.text.x=element_text(angle=90))+ggtitle("不同上证综指dividendyield未来一年收益平均值分布")



```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
