---
title: "R Notebook"
output: html_notebook
---

```{r}
syms<-c("000300.SH","000016.SH")

for(sy in syms){
  loadRData(sy)
}

alignSymbols(syms)





```

1. 指数不同点位下未来的收益
不同点位区间下，未来X天的收益，最大收益，最大亏损
最大收益和最大亏损计算有误，需调整
```{r}

source(file.path(substr(getwd(), 1, 22), "header.R"))

sym <- "000001.SH"
yieldDays <- 750


loadRData(sym)

applyInd(
  sym,
  fun.name = "Return.calculateX",
  arguments = list(x = get(sym), column = "close"),
  label = "dailyReturn"
)

applyInd(
  sym,
  fun.name = "rollapplyX",
  arguments = list(
    x = get(sym),
    column = "dailyReturn",
    width = yieldDays,
    FUN = "Return.cumulative"
  ),
  label = paste0("cumReturn", yieldDays, "D")
)

applyInd(
  sym = sym,
  fun.name = "rollapplyX",
  arguments = list(
    x = get(sym),
    column = "dailyReturn",
    width = yieldDays,
    FUN = "maxDrawdown"
  ),
  label = paste0("maxDown", yieldDays)
)


applyInd(
  sym = sym,
  fun.name = "rollapplyX",
  arguments = list(
    x = get(sym),
    column = "dailyReturn",
    width = yieldDays,
    FUN = "maxRunup"
  ),
  label = paste0("maxRunup", yieldDays)
)


applyInd(
  sym,
  fun.name = "leadX",
  arguments = list(
    x = get(sym),
    column = paste0("cumReturn", yieldDays, "D"),
    k = yieldDays
  ),
  label = paste0("leadR", yieldDays, "D")
)

applyInd(
  sym,
  fun.name = "leadX",
  arguments = list(
    x = get(sym),
    column = paste0("maxDown", yieldDays),
    k = yieldDays
  ),
  label = paste0("leadmaxD", yieldDays, "D")
)

applyInd(
  sym,
  fun.name = "leadX",
  arguments = list(
    x = get(sym),
    column = paste0("maxRunup", yieldDays),
    k = yieldDays
  ),
  label = paste0("leadmaxUp", yieldDays, "D")
) 

mydata<-as.data.frame(get(sym)[,c(4,5,13:15)])
names(mydata)<-c("close","pe","leadR","leadmaxD","leadmaxR")

mydata<-mydata%>%mutate(close.inter=cut(round(pe,0),15))%>%mutate(maxRD=leadmaxR/leadmaxD)

ydata<-mydata


ggplot(ydata,aes(x=close,y=leadR))+geom_point(shape=1)+
  geom_hline(aes(yintercept=0))+
  geom_vline(aes(xintercept=2900))+ggtitle("不同上证综指点位未来一年收益分布")
ggplot(ydata,aes(x=close,y=leadmaxR))+geom_point(shape=1)+
  geom_hline(aes(yintercept=0))+
  geom_vline(aes(xintercept=2900))+ggtitle("不同上证综指点位未来一年最大涨幅分布")
ggplot(ydata,aes(x=close,y=leadmaxD))+geom_point(shape=1)+
  geom_hline(aes(yintercept=0))+
  geom_vline(aes(xintercept=2900))+ggtitle("不同上证综指点位未来一年最大回撤分布")
ggplot(ydata,aes(x=close,y=maxRD))+geom_point(shape=1,size=0.5)+
  geom_hline(aes(yintercept=1))+
  geom_vline(aes(xintercept=2900))+ggtitle("不同上证综指点位未来一年最大涨幅比最大回撤分布")



ggplot(ydata,aes(x=pe,y=leadR))+geom_point(shape=1)+
  geom_hline(aes(yintercept=0))+
  geom_vline(aes(xintercept=13))+ggtitle("不同上证综指PE未来一年收益分布")
ggplot(ydata,aes(x=pe,y=leadmaxR))+geom_point(shape=1)+
  geom_hline(aes(yintercept=0))+
  geom_vline(aes(xintercept=13))+ggtitle("不同上证综指PE未来一年最大涨幅分布")
ggplot(ydata,aes(x=pe,y=leadmaxD))+geom_point(shape=1,size=0.5)+
  geom_hline(aes(yintercept=0))+
  geom_vline(aes(xintercept=13))+ggtitle("不同上证综指PE未来一年最大回撤分布")
  

ydata%>%group_by(close.inter)%>%summarise(mR=median(leadR,na.rm=T),mD=median(leadmaxD,na.rm=T),mU=median(leadmaxR,na.rm=T))
ggplot(ydata,aes(leadR))+facet_grid(close.inter~.)+geom_histogram(bins=100)


```



Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
